---
title: "In-Class Exercise 6"
description: |
  This contains the in-class work for Week 6.
author:
  - name: Che Xuan 
    url: https://www.linkedin.com/in/jacob-che-xuan-b646a9123/
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.retina = 3)
```

# Geographical Data

## Setting up R packages

```{r}
packages = c('tidyverse', 'knitr', 'sf', 'tmap', 'lubridate', 'clock', 'sftime', 'rmarkdown')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

## Importing Data

```{r}
schools <- read_sf("data/Schools.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
pubs <- read_sf("data/Pubs.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
buildings <- read_sf("data/Buildings.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
employers <- read_sf("data/Employers.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
restaurants <- read_sf("data/Restaurants.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
apartments <- read_sf("data/Apartments.csv", 
                   options = "GEOM_POSSIBLE_NAMES=location")
```

## Structure of Simple Point Feature

```{r}
print(schools)
```

## Structure of Simple Polygon Feature

```{r}
print(buildings)
```


## Plotting a Building Footprint Map

```{r}
tmap_mode("view")
tm_shape(buildings)+
tm_polygons(col = "grey60",
           size = 1,
           border.col = "black",
           border.lwd = 1)
tmap_mode("plot")
```

## Plotting a Composite Map

```{r}
tmap_mode("plot")
tm_shape(buildings)+
tm_polygons(col = "grey60",
           size = 1,
           border.col = "black",
           border.lwd = 1) +
tm_shape(employers) +
  tm_dots(col = "red")
```

# Movement Data

## Importing Data

```{r eval=FALSE}
logs <- read_sf("data/rawdata/ParticipantStatusLogs1.csv", 
                options = "GEOM_POSSIBLE_NAMES=currentLocation")
```

## Structure of Data Frame

```{r eval=FALSE}
glimpse(logs)
```

## Data Wrangling

```{r eval=FALSE}
logs_selected <- logs %>%
  mutate(Timestamp = date_time_parse(timestamp,
                                     zone = "",
                                     format = "%Y-%m-%dT%H:%M:%S")) %>%
  mutate(day = get_day(Timestamp)) %>%
  filter(currentMode == "Transport")
```

```{r eval=FALSE}
write_rds(logs_selected, "data/logs_selected.rds")
```

```{r}
logs_selected <- read_rds("data/logs_selected.rds")
```

## Computing the Hexagons

```{r}
hex <- st_make_grid(buildings, 
                    cellsize=100, 
                    square=FALSE) %>%
  st_sf() %>%
  rowid_to_column('hex_id')
plot(hex)
```

## Performing Point in Polygon Overlay

```{r}
points_in_hex <- st_join(logs_selected, 
                         hex, 
                         join=st_within)
plot(points_in_hex, pch='.')
```

## Performing Point in Polygon Count

```{r}
points_in_hex <- st_join(logs_selected, 
                        hex, 
                        join=st_within) %>%
  st_set_geometry(NULL) %>%
  count(name='pointCount', hex_id)
head(points_in_hex)
```

## Performing Relational Join

```{r}
hex_combined <- hex %>%
  left_join(points_in_hex, 
            by = 'hex_id') %>%
  replace(is.na(.), 0)
```

## Plotting the hexagon binning mapp

```{r}
tm_shape(hex_combined %>%
           filter(pointCount > 0))+
  tm_fill("pointCount",
          n = 8,
          style = "quantile") +
  tm_borders(alpha = 0.1)
```

## Creating Movement Path from Event Points

```{r}
logs_path <- logs_selected %>%
  group_by(participantId, day) %>%
  summarize(m = mean(Timestamp), 
            do_union=FALSE) %>%
  st_cast("LINESTRING")
```

```{r}
print(logs_path)
```

## Plotting the Movement Paths

```{r}
logs_path <- logs_selected %>%
  group_by(participantId, day) %>%
  summarize(m = mean(Timestamp), 
            do_union=FALSE) %>%
  st_cast("LINESTRING")
```


```{r}
logs_path_selected <- logs_path %>%
  filter(participantId==0)
tmap_mode("plot")
tm_shape(buildings)+
tm_polygons(col = "grey60",
           size = 1,
           border.col = "black",
           border.lwd = 1) +
  tm_shape(logs_path_selected) +
  tm_lines(col = "blue")
tmap_mode("plot")
```





