---
title: "Visual Analytics Project"
description: |
  I will explore the health of various employers in the city of Engagement, Ohio USA.
author:
  - name: Che Xuan 
    url: https://www.linkedin.com/in/jacob-che-xuan-b646a9123/
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.retina = 3)
```

# Overview

In this project, appropriate static and interactive statistical graphics methods are used to reveal the employment patterns of the [city of Engagement, Ohio USA](https://vast-challenge.github.io/2022/).

The data are processed by using appropriate **tidyverse** family of packages and the statistical graphics are prepared using **ggplot2** and its extensions.


# Installing & Launching R Packages

Before we get started, it is important for us to ensure that the required R packages have been installed. If yes, we will load the R packages. If they have yet to be installed, we will install the R packages and load them onto R environment.

The chunk code below will do the trick.

```{r}
packages = c('tidyverse', 'lubridate')

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

```

# Importing Data

The code chunk below imports *TravelJournal.csv* and *Employers.csv* from the data folder into R by using [`read_csv()`](https://readr.tidyverse.org/reference/read_delim.html) of [**readr**](https://readr.tidyverse.org/) package and save them as tibble data frames called *travel* and *employers*.

```{r}
participants <- read_csv("C:/Jacobche/ISSS608/th_ex/rawdata/Participants.csv")
checkin <- read_csv("C:/Jacobche/ISSS608/th_ex/rawdata/CheckinJournal.csv")
travel <- read_csv("C:/Jacobche/ISSS608/th_ex/rawdata/TravelJournal.csv")
employers <- read_csv("C:/Jacobche/ISSS608/th_ex/rawdata/Employers.csv")
jobs <- read_csv("C:/Jacobche/ISSS608/th_ex/rawdata/Jobs.csv")
```

# Data Wrangling

```{r}
checkin_work <- checkin %>%
  filter(venueType == 'Workplace')
```














